---
# title: "polmeth_outline"
# author: "Daniel Argyle"
# date: "6/12/2018"
# output: html_document
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/packages/svm-r-markdown-templates/svm-latex-ms.tex
title: "Legislator Arithmetic"
thanks: "The code for this method is available at the author's github repository."
author:
- name: Daniel Argyle
  affiliation: FiscalNote
abstract: "This document provides an introduction to R Markdown, argues for its..."
keywords: "ideal point estimation"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
# bibliography: ~/Dropbox/master.bib
# biblio-style: apsr
---

```{r setup, include=FALSE}
# Setup a python instance to use
library(reticulate)
```
wnom1
```{python, include=FALSE}
answer = '42'
```

# Introduction

# Existing methods
I come not to dismiss but to augment

[Insert the long illustrious history of ideal point estimation here]

# Technical Details

# Results

## My method and WNOMINATE packages are similar

## Let's do some things that weren't really feasible before

1. I implemented DW-NOMINATE as a neural network
    - Why? Because I could! But also because it's a nice platform for this kind of optimization.
    - It scales much better than existing implementations
    - It's extensible in very interesting ways
2. All ideal point models are (a bit) overfit.
    - At some point the algorithm starts to make marginal improvements to the parameters that don't improve out of sample performance
    - Out of sample performance matters much more than in sample (e.g. if we only cared about in sample we'd just add dimensions until we cam predict it perfectly)
    - Out of sample performance is a useful metric for evaluating modeling choices (adding another dimension, adding a time component, adding an external variable)

this is inline `r py$answer` and 

```{r}
py$answer
```

